\documentclass[a4paper,11pt, oneside]{book}
\usepackage[utf8]{inputenc}
\usepackage[francais]{babel}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{setspace}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage{etoolbox}
\usepackage{color}
\usepackage[explicit,pagestyles]{titlesec}
\usepackage[absolute,overlay]{textpos}
\usepackage{fancyhdr}
\usepackage{fontspec}
\usepackage{eurosym}
\usepackage{titlesec}


% ====== CONFIG ========

\setmainfont{Roboto Light}

\setmainfont{Roboto Light}
\setsansfont{Roboto}
\setmonofont{Roboto}
\newfontfamily\light{Roboto Slab Light}
\graphicspath{{img/}}
\setlength{\unitlength}{1mm}

\makeatletter

\definecolor{primary}{RGB}{44, 62, 80}


\titleformat{\chapter}[display]{\huge}{\thechapter \quad #1}{0pt}{}
\titlespacing{\chapter}{0pt}{0pt}{0pt}

\titleformat{\section}[display]{\LARGE}{}{0pt}{\thesection \quad #1}


\setlength{\TPHorizModule}{1mm}
\setlength{\TPVertModule}{1mm}
\def\sizeMedia{38}
\def\size{3.8cm}
\def\sizeMargin{0.2cm}
\def\margin{2}
\def\fixMargin{0}

\pagestyle{plain}

\author{Yann Prono, Quentin Tardivon}
\date{\today}

\def\school{TELECOM Nancy}
\def\schoolAddress{193 Avenue Paul Muller}
\def\schoolPostalCode{54602}
\def\schoolCity{Villers-lès-Nancy}
\def\schoolCodeAndCity{\schoolPostalCode, \schoolCity}
\def\schoolYear{2016 - 2017}

\def\appName{MyAdblock}

\def\schoolYear{2016 - 2017}

% ====== END CONFIG ========


\begin{document}

	\begin{titlepage}
		\input{cover}
	\end{titlepage}


	\newpage\newpage\null\thispagestyle{empty}
	\newpage
		\tableofcontents
		\thispagestyle{empty}


	\chapter{Introduction}

	\setcounter{page}{1}

Is this the fifteen time you passed the TOEIC test and you still didn't get it ?
Are you bored about making uninteresting tests on abandoned websites?
Do you want to improve your english level by listening dialogs of your preferred TV serie ?
Do you want to challenge others people about your language skills ?
Do you sing songs that you don't understand ?\\

\noindent English is everywhere: music, TV series, movies, articles, documentation, comics strip, social networks, youtube videos etc...
All these supports are gold nuggets. Indeed, a lot of people use these media in their daily lives in their native language.
Due to success of all these media and the utility for people, it can be possible to use some of them in order to learn a new language.\\

\noindent \appName \ is a quiz developed in the english courses context. It has been developed by students for students who want to test a new way to learn english.
Rules are simple: you have to answer a set of questions about general culture, grammar, listening comprehension, vocabulary... If you answer wrong 3 times, you lose and have to play again since the beginning of the quiz.
At the end of a quiz session, you have the possibility to share your score with others and measure your evolution.
In order to not be bored about the application, users have to possibility to suggest questions to expand the quiz.


\end{document}
